\ttlfnt{Comparing the performance of websites and their content distribution networks}

### 2016-08-27 Writeup/paper.tex
Fill out the Future work section

\section{Future Work}\label{sec:futurework}
\begin{itemize}
	\item Streaming (e.g incorporate youtube life or twitch non-vods)
	\item Video content vs video adverts
	\item Test from multiple locations
\end{itemize}

\pagebreak

>>>>

\section{Future Work}\label{sec:futurework}
Our experiments have focussed on streaming of internet video and audio on-demand, from websites including Youtube, Twitch.tv and Soundcloud. In future work we would like to extend this to streaming of live video and audio content such as from Youtube Live or Twitch.tv's live streams. Another extension would be to consider the differences in performance of streamed video content to video adverts, which are prevalent both on Youtube and Twitch.tv.

Another direction that would be useful in future work is to run a more distributed version of our experiments which include running the test from various locations around the world. This would give a better understanding of how our results generalize to the internet as a whole, rather than just the connectivity in South Africa.
